---
title: "Homework 1"
author: "Sophia Miller"
date: "9/19/2019"
output: github_document
---

# Loading tidyverse:

```{r}
library(tidyverse)
```
# Problem 1

## Creating a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”


```{r}
problem1_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("This", "is", "the", "first", "data", "science", "homework", "assignment"),
  vec_factor = factor(c("one", "two", "three", "one", "two", "three", "one", "two"))
)
```

# Taking the mean of each variable in the above data frame

```{r}
mean(pull(problem1_df, norm_samp))

mean(pull(problem1_df, norm_samp_pos))

mean(pull(problem1_df, vec_char))

mean(pull(problem1_df, vec_factor))
```

We are able only able to take the mean of the numeric and logical variables. We are unable to take the mean of the character and factor variables. 



