---
title: "Homework 1"
author: "Sophia Miller"
date: "9/19/2019"
output: github_document
---

# Loading tidyverse

```{r tidyverse}
library(tidyverse)
```
# Problem 1

## Creating a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 8
* a factor vector of length 8, with 3 different factor “levels”

```{r problem1_df}
problem1_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("This", "is", "the", "first", "data", "science", "homework", "assignment"),
  vec_factor = factor(c("one", "two", "three", "one", "two", "three", "one", "two"))
)
```

## Taking the mean of each variable in the above data frame:

```{r means}
mean(pull(problem1_df, norm_samp))

mean(pull(problem1_df, norm_samp_pos))

mean(pull(problem1_df, vec_char))

mean(pull(problem1_df, vec_factor))
```

*We are only able to take the mean of the numeric and logical variables. We are unable to take the mean of the character and factor variables.*

## Converting the logical, character and factor variables to numeric:

```{r convert_multiply, results = "hide"}
as.numeric(pull(problem1_df, norm_samp_pos))

as.numeric(pull(problem1_df, vec_char))

as.numeric(pull(problem1_df, vec_factor))
```

*After applying the "as.numeric" function, the logical vector is assigned values of 1 and 0, which indicate whether or not an element of the sample is greater than 0. The factor vector is assigned values of 1, 2 and 3, indicating which of the three factor levels an element belongs to. Now that these variables are assigned numeric values, we are able to take the mean.*

## Converting vector types and multiplying results by random sample:
##### Specifically, the code chunk below does the following:

* converts the logical vector to numeric, and multiplies the random sample by the result
* converts the logical vector to a factor, and multiplies the random sample by the result
* converts the logical vector to a factor and then converts the result to numeric, and multiplies the random sample by the result

```{r_convert_multiply}
log_num = as.numeric(pull(problem1_df, norm_samp_pos))

log_num * (pull(problem1_df, norm_samp))

log_fac = as.factor(pull(problem1_df, norm_samp_pos))

log_fac * (pull(problem1_df, norm_samp))

log_fac_num = as.numeric(as.factor(pull(problem1_df, norm_samp_pos)))

log_fac_num * (pull(problem1_df, norm_samp))
```

# Problem 2

## Creating a data frame comprised of :

* x: a random sample of size 500 from a standard normal distribution
* y: a random sample of size 500 from a standard normal distribution
* a logical vector indicating whether x + y >1 
* a numeric vector created by coercing the above logical vector
* a factor vector created by coercing the above logical vector

```{r problem2_df}
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = x + y > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical),
)
```

*There are `r nrow(problem2_df)` rows and `r ncol(problem2_df)` columns in the dataset. The mean, median, and standard deviation of x are `r mean(pull(problem2_df, x))`, `r median(pull(problem2_df, x))` and `r sd(pull(problem2_df, x))`, respectively. The proportion of cases for which x + y > 1 is `r mean(pull(problem2_df, vec_numeric))`.*

## Making a scatterplot of y vs. x; color points using logical variable:

```{r plot1}
ggplot(problem2_df, aes(x = x, y = y, color = vec_logical)) + geom_point()
```

## Exporting first scatterplot to project directory:

```{r plot_save}
ggsave("problem2_df.pdf")
```

## Making a scatterplot of y vs. x; color points using numeric variable:

```{r plot_2}
ggplot(problem2_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()
```

## Making a scatterplot of y vs. x; color points using factor variable:

```{r plot_3}
ggplot(problem2_df, aes(x = x, y = y, color = vec_factor)) + geom_point()
```

*The logical and factor variables have a value of either TRUE or FALSE. Therefore, in the first and third scatterplots, the blue dots represent the cases for which  the statment x + y > 1 is true, and the red dots represent the cases for which the statment x + y > 1 is false.* 

*The second scatterplot has a color scale ranging from 0 to 1, since it color points using the numeric variable. However, we only see two colors, the dark and light blue representing 0 and 1. This is because 0 and 1 are the only two possible values for the numeric variable; they correspond to the TRUE and FALSE values of the logical variable that was coerced to create the numeric variable.*


